\section{Introduction} \label{sec:intro}

% P1: Defintion of State machine replication (SMR) and its value on 
% fault-tolerance. Emphasis that SMR is especially useful to server
% applications that provide on-line service.

\emph{State machine replication (\smr)} models a program as a deterministic 
state machine, where the states are important program data and the transitions 
are deterministic executions of program code under input requests.  \smr runs 
replicas of the program and invokes a distributed consensus protocol (typically 
\paxos~\cite{paxos,paxos:simple,paxos:complex}) to ensure the same sequence of 
input requests for replicas, as long as a quorum (typically a majority) of the 
replicas agrees on the input request sequence. Under the deterministic execution 
assumption, this quorum of replicas must reach the same exact state despite 
replica failures or network partitions.  \smr is proven safe in 
theory and provides high availability in 
practice~\cite{paxos:live,paxos:practical,chubby:osdi,paxos:datastore, 
bolosky:nsdi11,mencius:osdi08,eve:osdi12,rex:eurosys14}.


% P2: Two problems makes it difficult to deploy general server programs
% in SMR. The first problem. is nondeterminism (thread interleavings,
% network requests arrivals).

The fault-tolerant benefit of \smr makes it particularly attractive on 
implementing a principled replication system for general programs, especially 
server programs that require high availability.  Unfortunately, doing so remains
quite challenging; the core difficulty lies in the deterministic state
machine abstraction required by \smr, elaborated below.

First, the deterministic execution assumption breaks down in today's
server programs because they are almost universally multithreaded. Even on the 
same exact sequence of input requests, different executions of the same exact 
multithreaded program may run into different thread interleavings, or 
\emph{schedules}, depending on such factors as OS scheduling and physical 
arrival times of requests. Thus, they can easily exercise different schedules 
and reach divergent execution states -- a difficult problem well recognized by 
the community~\cite{dos:osdi10,eve:osdi12,ddos:asplos13,rex:eurosys14}.
To tackle this problem, one prior approach,
execute-verify~\cite{eve:osdi12}, detects divergence of execution states
and retries, but it relies on developers to manually annotate states, a
strenuous and error-prone process.

Second, to leverage existing \smr systems such as
ZooKeeper~\cite{zookeeper}, developers often have to shoehorn their
programs into the narrowly defined state machine interfaces provided by
these \smr systems.  Ideally, experts -- those with intimate knowledge of
the arcane (think how many 
papers~\cite{paxos,paxos:simple,paxos:complex,paxos:live,paxos:practical} are 
needed to explain \paxos),
under-specified~\cite{paxos:practical} \smr protocols and subtle failure
scenarios in distributed systems -- should build a solid \smr system,
which all other developers then leverage. However, an \smr system often
has to settle for a specific state and transitional interface because it
cannot anticipate all possibilities in which developers structure their
programs.  For example, Chubby~\cite{chubby:osdi} defines a lock server
interface, and ZooKeeper a pseudo file system interface.  Orchestrating a
sever program into such a narrow interface not only requires
intrusive and error-prone modifications to the program's structure and
code, but also disrupts the \smr system itself at times. For instance,
developers abused Chubby for storage~\cite{chubby:osdi}, causing the
Chubby developers to add quota support.

% P5: Our goal, transparently replicate server programs. New replication
% abstraction: black-blox replication (BBRep). Key technique: DMT. Key 
% guarantee: TBD.

We present \xxx,\footnote{\xxx stands for Correctly ReplicAting
  Nondeterministic Executions. It is also our hope that our system is as
  elegant as the identically named bird.} an \smr system that
transparently replicates server programs for high availability.  With
\xxx, a developer focuses on implementing her program's intended
functionality, not replication.  When she is ready to replicate her
program for availability, she simply runs \xxx with her program on
multiple replicas.  Within each replica, \xxx interposes on the socket and
the thread synchronization interfaces to keep replicas in sync.
Specifically, it considers each incoming socket call (\eg, \accept a
client's connection or \recv a client's data) an input request, and
runs a \paxos consensus protocol~\cite{paxos:practical} to ensure that a
quorum of the replicas sees the same exact sequence of the incoming socket calls.

% It schedules all thread synchronizations (\eg, \mutexlock)
% deterministically to ensure that, even with multithreading, the same input
% stream leads to the same execution state. It leverages transparent 
% process and file system checkpoint tools to recover or add replicas.

%% Our design of \xxx avoids intrusive modifications to a server program, and is 
%% efficient because \xxx intercepts only a server program's socket calls and 
%% thread synchronizations, allowing the other code to run in parallel. Due to 
%% this design's elegance, we name our system after crane, one of the most elegant 
%% birds.

To address nondeterminism, we have built three \emph{deterministic 
multithreading (\dmt)} systems~\cite{cui:tern:osdi10, peregrine:sosp11, 
parrot:sosp13}. \dmt~\cite{dpj:oopsla09,dmp:asplos09,kendo:asplos09,
coredet:asplos10, 
dos:osdi10,ddos:asplos13,ics:oopsla13} typically maintains a \emph{logical 
time}\footnote{Though related, the logical time in \dmt is not to 
be confused with the logical time in distributed systems~\cite{lamportclock}.} 
that advances deterministically on each thread's synchronization. By 
serializing thread synchronizations, \dmt practically makes an entire 
multithreaded execution deterministic. The overhead of \dmt is typically 
moderate because most code is not synchronization and can still run in parallel. 
Specifically, \xxx leverages \parrot~\cite{parrot:sosp13}, our latest \dmt 
system. \parrot incurs merely 12.7\% overhead in 
average on a wide range of 108 popular multithreaded programs on 24-core 
machines.

A key challenge on realizing \smr for multithreaded executions is that,
simply combining \paxos and \dmt is not sufficient to keep replicas in
sync, because the physical time that each request arrives at different
replicas may still be different, easily leading to divergence of execution
states and outputs.

%% For instance, consider multiple server threads blocking at \recv to 
%% wait for \send socket calls issued from clients. Even if \paxos ensures the 
%% same order of these \send calls among replicas, network delays and OS 
%% scheduling in different replicas can still easily cause various return 
%% orders of these \recv calls and thus inconsistent outputs (confirmed in 
%% our evaluation; see \S\ref{sec:correctness}). To keep replicas in sync, we must handle 
%% each client's socket call with the server's matching blocking call at the 
%% same logical time because request timing variations can lead to different 
%% schedules.

Two prior approaches attempted to tackle this challenge.  
Execute-agree-follow~\cite{rex:eurosys14} records a partially
ordered schedule of \pthread synchronizations on one replica and replays it 
on the other replicas, which may incur high network bandwidth 
consumption and performance overhead. dOS~\cite{dos:osdi10} also leverages
\dmt for replication, but it determines the logical admission time for
each request using two-phase commit.  Aside from two-phase commit's known
intolerance of primary failures, per-request commit is also costly.

One may consider solving this challenge by leveraging the underlying
distributed consensus protocol to determine the logical admission time for each
request.  Specifically, when running the consensus protocol to decide each
request's position in the request sequence, a predicted logical admission time 
can be carried as part of the decision as well. Unfortunately, 
predicting a logical admission time for each request accurately is quite 
challenging because typical server programs have background threads which 
may frequently tick logical clocks. A too-small predication leads to 
replica divergence if another replica has already run past the predicted 
logical time. A too-large predication blocks the system unnecessarily 
because replicas cannot admit the request before reaching the predicted time.

Our key insight is that many requests need no admission time consensus
because their admission times are already deterministic.  Hypothetically,
if the requests arrive faster than they are admitted at each replica, each
request's admission time is fully deterministic because each replica
simply admits requests as fast as it can. In practice, requests do not arrive 
this fast.  However, there are still frequent bursts of requests that arrive 
together. Among replicas, as long as the first request of a burst is admitted at 
a deterministic logical time, all the other requests in the burst are admitted 
at deterministic logical times without requiring consensus.

Leveraging this insight, we created an technique called \emph{\timealgo} to 
enforce deterministic logical times efficiently.  It ensures that the 
first request in a burst is admitted at each replica deterministically by 
inserting a deterministic wait after the previous burst of requests are all 
admitted.  During this wait, each replica only processes already admitted 
requests, and does not admit new requests.  \xxx negotiates a consistent 
duration of the wait via the underlying distributed consensus protocol, and 
enforces this wait at each replica via \dmt.  These waits are like 
deterministic time bubbles between bursts of requests (hence the name of the 
technique), creating the illusion that the requests arrive faster than they are 
admitted.

In short, by converting per-request admission time consensus to per-burst,
\timealgo efficiently combines the input determinism of \paxos and the
execution determinism of \dmt.  For busy servers, requests in bursts
greatly outnumber the other requests.  (We observed that \timebubblelow to
\timebubblehigh of requests are in bursts; see \S\ref{sec:overhead}.) They
rarely need to invoke time consensus, enjoying good performance.  For idle
servers, time consensus overhead does not matter much because the servers
are idle anyway.

% Heming: todo: move this to the time bubble section.
% In a conceptual level, \xxx enforces the same logical times for network
% requests across different replicas with three rules. First, \paxos
% ensures the same totally ordered sequence of network requests and
% inserted time bubbles as a ``\paxos operation queue" for each replica node.
% Second, \dmt guarantees that it only ticks logical clocks (\ie,
% schedules synchronizations) only when this queue is not empty. Third, the 
% \timealgo technique ensures that this queue is not empty (if empty, it 
% inserts time bubbles).


% P10: Evaluation highlights.
We implemented \xxx by interposing on the POSIX socket and the \pthread
synchronization interfaces.  It intercepts operations along these
interfaces by hijacking dynamically linked library calls for transparency.
It implements the \paxos protocol atop libevent~\cite{libevent} for
distributed consensus, and leverages our \parrot system for deterministic
multithreading.  Unlike prior \smr systems with narrow interfaces, \xxx's
checkpoint and recovery must work with general programs. To this end, it
leverages \criu~\cite{criu} to checkpoint and restore process states, and
\lxc~\cite{lxc} for file system states.  An additional benefit of using
the \lxc container is that \xxx isolates the replicated server program
from the environment, avoiding nondeterministic systems resource contentions.

% (\eg,
% a random external process grabs the network port the replicated program
% needs).

We evaluated \xxx on \nprog widely used server programs,
including \http servers \apache and \mongoose, an anti-virus server
\clamav, a \upnp multimedia server \mediatomb, and a database server \mysql. 
Our results on popular performance benchmarks show that \xxx works with
all the servers easily (three servers require no modification, and the
other two servers each require only two lines of \parrot hints~\cite{parrot:sosp13}
to improve performance); that \xxx's performance overhead is
moderate (an average of \overhead overhead at the servers' peak 
performance setups on our 24-core machines); and that \xxx is robust on replica 
failures.

In the remainder of this report, \S\ref{sec:overview} introduces \xxx's 
architecture. \S\ref{sec:eval} presents evaluation results. 
\S\ref{sec:conclusion} concludes, and \S\ref{sec:recommendation} presents 
recommendations.



























