Major iterms:

1. Find a good example. Illustrate the benefit of per-burst consensus vs. per 
request consensus. Workload: one put and and get. dont' say curl, just a 
simplified client.
  Key points (entropy) to make in this example:
  (1) [done] Timebubble component is essential for determinism (or 
consistency). If disable this component, output is inconsistent across 
replicas. Confirmed in correctness evaluation.
  (2) [done] Timebubble mechanism is also essential for correctness (forward 
progress) in our system. Otherwise while the worker threads are serving 
requests, client's CLOSE() have not come yet, they can not proceed and execute 
pthreads synchronizations, or proceed inconsistently across replicas. They need 
time bubbles to consistently proceed across replicas.
  (3) [done] Per-request consensus for logical clock is not necessary (aka 
timebubble is efficient). Justified by eval, low percentage of timebubbles. 
  


2. [done] Why are the applications we evaluated require SMR? First, these 
applications 
already have critical internal storage. Either file storage or database 
storage. Second, according to the reviewers' comments, even developers can 
separate the storage and frontend servers, this process requires lots of expert 
knowledge. It would be great if we can have CRANE to do this automatically.

3. [done] Correctness evaluation. Output sequence.

4. Sensitivity of our CRANE systems parameters. Size of big and small 
timebubbles.

5. [mostly done] Added lxc checkpoint description. Intro, Overview, Impl, Eval 
[todo].


Minor items:

1. [done, timing channels] Other broader applications of time bubbling? 
Avoiding time channels?

2. [done, in intro] Scope of our runtime systems. Current implementation 
supports POSIX, and can be extended to other runtimes.

3. [done] Mention that we can also handle read-only requests, but just not 
necessary 
because currently the performance overhead is already low.

4. [done, emphasis dOS applies DMT] DDOS's single point of failures.

5. Chubby. Is it a file system service or lock service?

6. [done, added to intro] Is determinism a key difficulty of SMR? Yes, 
recognized by the community (cite dOS, DDOS, REX, and EVE).

7. [done] Can other consensus procotols such as Raft be used in our system? Yes, as 
long as they can enforce a consistent sequence of input requests.

8. [done] Add app of CRANE on making program analyses more effective.
  [no need] Intro. Mention this. Enable "multiple" analysese within one 
execution.
  [done] Discussion. Mention in more details.
  
9. [done] Remove the server bootstraps assumption from text. We have 
implemented it.

10. [done] Refine workloads description in the beginning of eval. Range from 
CPU to IO bounds, diverse servers.

11. [done] Why is the system named CRANE?